### 2025-05-30 docs/article/Sections/results.tex
Update article results to Github workflow results

All the following benchmarks were conducted on a local machine running Ubuntu
22.04 LTS with a 6-core, 12-thread CPU and 32GB of RAM\@. All tests were
conducted on the OpenJDK VM Corretto 21. The JVM was configured with a minimum
heap size of 1024MB and a maximum heap size of 16GB\@.

@@

The results show that when using the blocking template engines with a separate
coroutine dispatcher, the engines are unable to scale effectively beyond 16
concurrent users. In contrast, the non-blocking engines scale effectively up to
128 concurrent users, with HtmlFlow achieving approximately 11,000 requests per
second. When using the blocking approaches in the context of Virtual Threads
(achieving non-blocking I/O), the engines scale effectively up to 128
concurrent users, with Jstachio matching HtmlFlow`s performance at
approximately 11,000 requests per second. Thymeleaf, using the reactive View
Resolver driver, also scales to 128 users, albeit less effectively, achieving
around 8,500 requests per second.

@@

% The results for the Spring MVC implementation, shown in
% Figure~\ref{fig:presentations-springmvc-jmeter}, compare two approaches:
% \textit{Blocking}, which uses platform threads with \texttt{StreamingResponseBody},
% and \textit{Virtual}, which uses Virtual Threads. Both approaches scale
% effectively up to 128 concurrent users, with the Virtual Thread approach
% achieving a slightly higher throughput of 9,000 requests per second. However,
% these values are slightly lower than those observed in the Spring WebFlux
% implementation.

The results for the Spring MVC implementation, shown in
Figure~\ref{fig:presentations-springmvc-jmeter}, compare two synchronous
approaches: \textit{Blocking}, which uses platform threads with
\texttt{StreamingResponseBody}, and \textit{Virtual}, which uses Virtual
Threads. Note that for Spring MVC, which follows a thread-per-request
architecture, neither of the asynchronous approaches—\textbf{Reactive} nor
\textbf{Suspendable}—described in Section~\ref{sec:bench} are applicable. Regarding the
synchronous strategy, both \textit{Blocking} and \textit{Virtual} scale
effectively up to 128 concurrent users, with the Virtual Threads approach
achieving a slightly higher throughput of approximately 9,000 requests per
second. However, these values are slightly lower than those observed in the
Spring WebFlux implementation.

@@

The results for the Quarkus implementation, shown in
Figure~\ref{fig:presentations-quarkus-jmeter}, indicate that Quarkus handles
synchronous approaches more efficiently than Spring WebFlux. The blocking
engines scale up to 128 concurrent users, achieving up to 10,000 requests per
second. While the use of Virtual Threads results in a slightly higher
throughput, the difference is negligible, with both approaches delivering
comparable performance.

Additionally, \textit{HtmlFlow-Rx}, a reactive implementation of the HtmlFlow
template engine (equivalent to the approach shown in
Listing~\ref{lst:presentation-observable}) that utilizes Quarkus's reactive
programming model, achieved throughput similar to the \textit{Blocking} and
\textit{Virtual}
approaches—approximately 10,000 requests per second. This demonstrates that
Quarkus's reactive programming model is effective for enabling PSSR\@. However,
there is no significant difference in performance between the reactive and
synchronous approaches, indicating that the reactive model does not provide a
substantial advantage over synchronous approaches in this context.

@@

The results in Figure~\ref{fig:stocks-webflux-jmeter} use the same template
engines and approaches as the previous benchmark, but replace the data model
with the more complex Stock class, including 20 instances. Despite the
increased complexity and number of instances, the scalability of the engines
remains largely unaffected. However, throughput is reduced by approximately 50
percent across all engines, with HtmlFlow achieving 6,000 requests per second.
Since the \texttt{Stock} class\ contains more data properties than the
\texttt{Presentation} class, the data binding to the template engine adds
overhead, which explains the reduced performance. The Thymeleaf implementation
using the reactive View Resolver driver reaches 5,000 requests per second,
suggesting that the performance drop compared to the Presentation benchmark is
not substantial.

@@

The results observed in Figure~\ref{fig:stocks-springmvc-jmeter} show that the
Spring MVC implementation using the blocking approach with
\texttt{StreamingResponseBody} achieves a throughput of up to 5500 requests per
second, while no significant change is observed when using Virtual Threads. As
such, both approaches scale effectively up to 128 concurrent users.

@@

The results depicted in Figure~\ref{fig:stocks-quarkus-jmeter} show that the
Quarkus implementation scales effectively up to 128 concurrent users, achieving
performance comparable to the Spring WebFlux implementation. The blocking
engines reach approximately 5,500 requests per second, and once again, there is
no significant difference between the \textit{Blocking} and \textit{Virtual}
approaches, with both achieving similar results.

In addition to the blocking engines, the \textit{HtmlFlow-Rx} approach also
achieves a throughput of approximately 5,500 requests per second, matching the
performance of the \textit{Blocking} and \textit{Virtual} approaches. This
further demonstrates that there is no significant difference in performance
between the reactive and synchronous approaches in this context.

>>>>

All the following benchmarks were conducted on a Github-hosted virtual machine
under GitHub Actions, running Ubuntu 22.04 LTS with a 4-core, 8-thread CPU and
16GB of RAM\@. All tests were conducted on the OpenJDK VM Corretto 21. The JVM
was configured with a minimum heap size of 512MB and a maximum heap size of
16GB\@.

@@

The results in Figure~\ref{fig:presentations-webflux-jmeter} show that when
using blocking template engines with a separate coroutine dispatcher, the
engines are unable to scale effectively beyond 4 concurrent users. In contrast,
the non-blocking engines scale efficiently up to 128 concurrent users, with
HtmlFlow achieving 4,487 requests per second. When blocking approaches are
executed in the context of Virtual Threads—thus enabling non-blocking I/O—the
engines also scale up to 128 concurrent users, with Jstachio using Virtual
Threads reaching 3,514 requests per second. The Thymeleaf implementation using
the reactive View Resolver driver also scales up to 128 concurrent users, but
achieves a lower throughput of approximately 2,559 requests per second.

It is important to note that the differences in scalability and throughput
between the \textit{HtmlFlow-Susp}, \textit{Jstachio-Virtual}, and
\textit{Thymeleaf-Rx} approaches may be influenced by the specific template
engines used, rather than the approach itself. When comparing the
\textit{Reactive}, \textit{Suspendable}, and \textit{Virtual} approaches
specifically with HtmlFlow, we found that all three achieve similar
performance: HtmlFlow using a blocking approach with Virtual Threads reaches
4,691 requests per second, while HtmlFlow using a reactive approach achieves
4,792 requests per second.

@@

% The results for the Spring MVC implementation, shown in
% Figure~\ref{fig:presentations-springmvc-jmeter}, compare two approaches:
% \textit{Blocking}, which uses platform threads with \texttt{StreamingResponseBody},
% and \textit{Virtual}, which uses Virtual Threads. Both approaches scale
% effectively up to 128 concurrent users, with the Virtual Thread approach
% achieving a slightly higher throughput of 9,000 requests per second. However,
% these values are slightly lower than those observed in the Spring WebFlux
% implementation.
The results for the Spring MVC implementation, shown in
Figure~\ref{fig:presentations-springmvc-jmeter}, compare two synchronous
approaches: \textit{Blocking}, which uses platform threads with
\texttt{StreamingResponseBody}, and \textit{Virtual}, which uses Virtual
Threads. Since Spring MVC follows a thread-per-request architecture, the
asynchronous approaches—\textbf{Reactive} and \textbf{Suspendable}—described in
Section~\ref{sec:bench} are not applicable. Both the \textit{Blocking} and
\textit{Virtual} strategies scale effectively up to 128 concurrent users, with
the Virtual Threads approach achieving a slightly higher maximum throughput of
2,797 requests per second, compared to 2,498 requests per second for the
blocking approach. These results indicate that while Spring MVC can handle a
moderate level of concurrency, it does not reach the scalability of the
reactive or suspendable approaches available in Spring WebFlux. Furthermore,
Spring MVC does not enable Progressive Server-Side Rendering (PSSR) for the
tested templates, as previously discussed in Section~\ref{sec:bench}.

@@

The results for the Quarkus implementation, shown in
Figure~\ref{fig:presentations-quarkus-jmeter}, indicate that Quarkus handles
synchronous approaches more efficiently than Spring WebFlux. The blocking
engines scale up to 128 concurrent users, achieving up to 3744 requests per
second. When using Virtual Threads, the throughput increases even further,
reaching 4856 requests per second. This demonstrates that Quarkus's
implementation of Virtual Threads is effective for enabling PSSR\@, and
comparable to the \textit{Suspendable} and \textit{Reactive} used approaches in
Spring WebFlux in terms of scalability and throughput.

Additionally, \textit{HtmlFlow-Rx}, a reactive implementation of the HtmlFlow
template engine (equivalent to the approach shown in
Listing~\ref{lst:presentation-observable}) that utilizes Quarkus's reactive
programming model, achieved a lower throughput than the the \textit{Blocking}
and \textit{Virtual} approaches—3088 requests per second. This demonstrates
that Quarkus's reactive programming model is effective for enabling PSSR\@,
although it does not achieve the same level of performance as the same approach
in Spring WebFlux.

@@

The results in Figure~\ref{fig:stocks-webflux-jmeter} use the same template
engines and approaches as the previous benchmark, but replace the data model
with the more complex Stock class, including 20 instances. When using this data
model, we observe that the scalability of the engines is not significantly
affected, however the throughput is reduced across all engines. When compared
to the Presentation benchmark, we observe that particularly the approaches
using Virtual Threads took a greater performance hit when compared to the
\textit{Reactive} and \textit{Suspending} approaches, with Jstachio using
Virtual Threads now achieving 1509 requests per second, compared to the 1,750
requests per achieved by the Thymeleaf implementation using the reactive View
Resolver driver.

It is again important to note that the differences in scalability and
throughput between the \textit{HtmlFlow-Susp}, \textit{Jstachio-Virtual}, and
\textit{Thymeleaf-Rx} approaches may be influenced by the specific template
engines used, rather than the approach itself. When comparing the
\textit{Reactive}, \textit{Suspendable}, and \textit{Virtual} approaches
specifically with HtmlFlow, we found that all three achieve similar
performance: HtmlFlow using a blocking approach with Virtual Threads reaches
3,090 requests per second, while HtmlFlow using a reactive approach achieves
3,026 requests per second.

The overall throughput reduction is expected, as the Stock class contains more
data properties than the \texttt{Presentation} class, adding overhead related
to the data binding process of each template engine.

@@

The results shown in Figure~\ref{fig:stocks-springmvc-jmeter} indicate that the
Spring MVC implementation using the blocking approach with
\texttt{StreamingResponseBody} achieves a throughput of up to 1,916 requests
per second, with no significant improvement observed when using Virtual
Threads. Both approaches scale effectively up to 128 concurrent users. Although
these approaches achieve higher throughput in Spring MVC than in Spring
WebFlux, their overall performance remains lower than that of the reactive and
suspendable approaches.

@@

The results depicted in Figure~\ref{fig:stocks-quarkus-jmeter} show that the
Quarkus implementation scales effectively up to 128 concurrent users, achieving
performance comparable to the Spring WebFlux implementation. The blocking
approach reaches a throughput of 3,019 requests per second, while the Virtual
Threads approach achieves a throughput of 3,357 requests per second.

In addition to the blocking engines, the \textit{HtmlFlow-Rx} approach also
achieves a throughput of 1760 requests per second, indicating that this
approach achieves lower performance in Quarkus than in Spring WebFlux, where it
reached 3,026 requests per second, as previously mentioned.
